%===============================================================================
% Sebastian
%===============================================================================

\subsection{CV for Sebastian Achilles}


\begin{description}
\item[] J\"ulich Supercomputing Centre (JSC)
\item[] Forschungszentrum J\"ulich GmbH
\item[] Wilhelm-Johnen-Stra{\ss}e
\item[] 52425 J\"ulich (Germany)
\item[] s.achilles@fz-juelich.de
\end{description}

\subsection*{Education}

\begin{description}
\item[] M.Sc. Simulation Sciences, RWTH Aachen University.
\item[] B.Sc. Physics, 2014, RWTH Aachen University.
\end{description}

\subsection*{Professional Experience}

\begin{description}
\item[] 2022 - present: HPC and Cloud System engineer, Jülich Supercomputing Center (JSC), Forschungszentrum
–present Jülich GmbH, Jülich.
\item[] 2020 - 2022: Research Assistant, Jülich Supercomputing Center (JSC), Forschungszentrum
–present Jülich GmbH, Jülich.
\item[] 2017 - 2020: Postgraduate student, Aachen Institute for Advanced Study in Computational Engineering Science (AICES), RWTH Aachen University, Aachen.

\end{description}

\subsection*{Tools}

\begin{itemize}
\item[] \textbf{EasyBuild}: (scientific) software build and installation framework
\item[] Developer (2021 - present)
\item[] \url{https://easybuild.io}
\end{itemize}

\subsection*{Conferences, Workshops and Tutorials}
\begin{itemize}
\item[] \emph{Maintaining a Modern Scientific Software Stack Made Easy with EasyBuild} tutorial at ISC'22, June 2022 (\url{https://easybuild.io/tutorial/isc22})
\end{itemize}

\subsection*{Selected Publications}

\paragraph{Conference Papers}

\begin{itemize}
\item[] Estela Suarez, Wolfgang Frings, Norbert Attig, Sebastian Achilles, Jacopo De Amicis, Thomas
Eickermann, Eric Gregory, Björn Hagemeier, Andreas Herten, Jenia Jitsev, Dorian Krause,
Edoardo Di Napoli, Jan Meinke, Kristel Michielsen, Bernd Mohr, Dirk Pleiter, Alexandre
Strube, and Thomas Lippert. \emph{Developing Exascale Computing at JSC.} NIC Symposium
2020. Vol. 50. Publication Series of the John von Neumann Institute for Computing (NIC)
NIC Series. NIC Symposium 2020, Jülich (Deutschland).
\end{itemize}

\paragraph{Journal Papers}

\begin{itemize}
  \item [] Jonas B. Hauck, Carsten Honerkamp, Sebastian Achilles, and Dante M. Kennes. \emph{Electronic
instabilities in Penrose quasi-crystals: competition, coexistence and collaboration of order.} Aug. 31, 2020.
  \item[] Xiao Zhang, Sebastian Achilles, Jan Winkelmann, Roland Haas, André Schleife, and Edoardo Di
Napoli. \emph{Solving the Bethe-Salpeter equation on massively parallel architectures.} June 15, 2020.
\end{itemize}


\newpage
