%===============================================================================
% Alan
%===============================================================================

\subsection{CV for Alan \'O Cais}

\begin{description}
\item[] Centre Européen de Calcul Atomique et Moléculaire (CECAM)
\item[] Avenue de Forel 2, BCH 3103
\item[] 1015 Lausanne, Switzerland
\item[] alan.ocais@cecam.org
\end{description}

\subsection*{Education}

\begin{description}
\item[] Ph.D Theoretical Physics, 2005, Trinity College Dublin (Ireland)
\item[] M.Sc. High Performance Computing, 2002, Trinity College Dublin (Ireland)
\item[] B.Sc. Theoretical Physics, 2001, Trinity College Dublin (Ireland)
\end{description}

\subsection*{Professional Experience}

\begin{description}
\item[] 2022 - present: Scientific Software Engineer with CECAM
\item[] 2016 - 2021: E-CAM Centre of Excellence Software Manager at J\"ulich Supercomputing Centre (Germany)
\item[] 2010 - 2016: Research Fellow at J\"ulich Supercomputing Centre (Germany)
\item[] 2008 - 2010: Scientific Coordinator at The Cyprus Institute (Cyprus)
\item[] 2006 - 2008: Research Fellow at University of Adelaide (Australia)
\item[] 2005 - 2006: Research Fellow at Trinity College Dublin (Ireland)
\end{description}

\subsection*{Tools}

\begin{itemize}
\item[] \textbf{EasyBuild}: (scientific) software build and installation framework
\item[] Developer (2013 - present) -- \url{https://easybuild.io}
\end{itemize}

\subsection*{Conferences, Workshops and Tutorials}
\begin{itemize}
\item[] \emph{Maintaining a Modern Scientific Software Stack Made Easy with EasyBuild} tutorial at ISC'21, June 2021 (\url{https://easybuild.io/tutorial})
\item[] Organiser of the first \emph{European HPC Training Stakeholder Workshop} (in coordination with the European Commission)
\item[] Instructor at all E-CAM Centre of Excellence \emph{\href{https://www.e-cam2020.eu/events?tribe_paged=1&tribe_event_display=list&tribe-bar-date=2015-10-01&tribe-bar-search=Extended}{Extended Software Development Workshops}}
\item[] Local organizer of the \emph{\href{https://github.com/easybuilders/easybuild/wiki/2nd-EasyBuild-User-Meeting}{2nd EasyBuild User Meeting (EUM'17)}}. J\"ulich. Germany.
\item[]Invited instructor at PRACE seasonal training workshops:
\begin{itemize}
\item[]  PRACE Autumn School in HPC Programming Techniques, Athens 25-28 November 2014: Lectures on Profiling and Optimization and Benchmarking
\item[]  PRACE Winter School, Tel Aviv 10-13 February 2014: Lectures on Profiling and Optimization and Benchmarking
\item[] Joint HP-SEE, LinkSCEEM-2 and PRACE HPC Summer Training, Athens 13-15 July 2011: Lectures on Profiling and Optimization and Benchmarking
\end{itemize}
\end{itemize}

\subsection*{Selected Publications}

\paragraph{Conference Papers}

\begin{itemize}
\item[] A. \'O Cais, P. Steinbach, \emph{Expanding user communities with HPC Carpentry}. Proceedings of the Workshop on HPC Education and Training for Emerging Technologies at ISC2019, Journal of Computational Science Education. 11. 21-25.
\end{itemize}

\begin{itemize}
\item[] D. Alvarez, A. O'Cais, M. Geimer, K. Hoste, \emph{Scientific Software Management in Real Life: Deployment of EasyBuild on a Large Scale System}. Proceedings of the 3rd International Workshop on HPC User Support Tools, Salt Lake City, USA, 2016.
\end{itemize}

\paragraph{Journal Papers}

\begin{itemize}
\item[] B. Dröge, V. Holanda Rusu, K. Hoste, C. van Leeuwen, A. O'Cais, T. Röblitz, \emph{{EESSI}: {A cross‐platform
    ready‐to‐use optimised scientific software stack}}. Software: Practice and Experience, 53(1):176-210, Jan. 2022,
    \url{https://doi.org/10.1002/spe.3075}
\item[] MJT Oliveira, N Papior, Y Pouillon, V Blum, E Artacho,\dots, \emph{The {CECAM} electronic structure library and the modular software development paradigm}.
  J Chem Phys. 2020;153:024117
\item[] M.S. Mahbub, (Adelaide U. \& Rajshahi U.), Alan O'Cais, Waseem Kamleh, B.G. Lasscock, Derek B. Leinweber, Anthony G. Williams, \emph{Isolating Excited States of the Nucleon in Lattice QCD}, Phys.Rev.D80:054507,2009.
\item[] M.S. Mahbub, (Adelaide U. \& Rajshahi U.) , Alan O'Cais, Waseem Kamleh, Ben G. Lasscock, Derek B. Leinweber, Anthony G. Williams, (Adelaide U.), \emph{Isolating the Roper Resonance in Lattice QCD}, Phys.Lett.B679:418-422,2009.
\item[] Alexandrou, C., et al., \emph{Evaluation of fermion loops applied to the calculation of the n' mass and the nucleon scalar and electromagnetic form factors}, Computer Physics Communications 183.6 (2012): 1215-1224.
\item[] J. Foley, K. Jimmy Juge, A. O'Cais, M. Peardon, S.M. Ryan and J. I. Skullerud, \emph{Practical all-to-all propagators for lattice QCD}, Comput. Phys. Commun. 172 (2005) 145.
\end{itemize}

\newpage
