%===============================================================================
% Jakob
%===============================================================================

\subsection{CV for Jakob Blomer}
\begin{description}
\item[] CERN
\item[] 1211 Geneva 23
\item[] jblomer@cern.ch
\end{description}

\subsection*{Education}
\begin{description}
    \item[] PhD in Computer Science, 2012, Technical University of Munich (Germany)
    \item[] Masters in Computer Science, 2008, University of Karlsruhe (Germany)
\end{description}

\subsection*{Professional Experience}
\begin{description}
    \item[] 2020--: Leading the R\&D effort on the future event data I/O for experiments at the CERN LHC (CERN)
    \item[] 2015--2023: Project leader of the CernVM File System (CERN)
    \item[] 06/2014--09/2014: Visiting Scholar in the RAMCloud research group (Stanford University)
    \item[] 2012-2014: Fellow (CERN)
\end{description}

\subsection*{Tools}

\begin{itemize}
    \item[] CernVM File System: global-scale file system for software distribution
    \\lead developer (2012--2023)
    \\{\small{\url{https://cernvm.cern.ch}}}
    \item[] ROOT RNTuple: columnar I/O system for particle physics event data\\lead developer (2018--)\\{\small{\url{https://root.cern}}}
\end{itemize}

\subsection*{Conferences, Workshops and Tutorials}

\begin{itemize}

\item[] (co-)organisation of \emph{CernVM} workshops in
    \href{https://indico.cern.ch/event/1079490}{Amsterdam (2022)},
        \href{https://indico.cern.ch/event/757415/}{Geneva (2019)},
        \href{https://indico.cern.ch/event/469775/}{Oxford (2016)}.

\end{itemize}

\subsection*{Selected Publications}

\paragraph{Conference Presentations}

\begin{itemize}

\item[] J. Blomer, \emph{Advances in software management tools}. Large Hadron Collider Physics Conference (LHCP), Paris, France, 2021.

\item[] J. Blomer, \emph{CERN’s Virtual File System for Global-Scale Software Delivery}. Int. Conf. Massive Storage Systems and Technology (MSST), Santa Clara, USA, 2019.

\item[] D. Abdurachmov, J. Blomer,
\emph{High Energy Physics and ARMv8 64-bit? Investigating the Future of Computing at CERN}.
Linaro Connect, Budapest, Hungary, 2017.

\item[] J. Blomer, A. Harutyunyan, \emph{A Novel Approach for Distributing and Managing Container Images}. MesosCon North America, Denver, USA, 2016.

\item[] J. Blomer, \emph{Experiences on File Systems: Which is the best file system for you?}. Computing in High Energy and Nuclear Physics (CHEP), Okinawa, Japan, 2015.

%\item[] J. Blomer, \emph{Keynote: Experiences in using Virtual Machines for High-Throughput Computing at the CERN LHC}. Computing in High Energy and Nuclear Physics (CHEP), Okinawa, Japan, 2015.

\end{itemize}

\paragraph{Journal Articles}

\begin{itemize}

\item[] V. Padulano, E. Tejedor, P. Alonso-Jordà, J. Lopez Gomez, J. Blomer,
\emph{A caching mechanism to exploit object store speed in High Energy Physics analysis}.
Cluster Computing, 25(5). 2022

\item[] C. Lange, J. Blomer, S. Mosciatti, \emph{Increasing the Execution Speed of Containerized Analysis Workflows Using an Image
Snapshotter in Combination With CVMFS}. Frontiers in Big Data 4. 2021

\item[] J. Blomer, G. Ganis, N. Hardi, R. Popescu, \emph{Delivering LHC software to HPC compute elements with CernVM-FS}.
Lecture Notes in Computer Science, 10524. 2017.

\item[] P. Buncic, C. Aguado-Sanchez, J. Blomer, A. Harutyunyan, M. Mudrinic,
\emph{A practical approach to virtualization in HEP}.
The European Physical Journal Plus, 126(1). 2011.

\end{itemize}
