%===============================================================================
% Valentin
%===============================================================================

\subsection{CV for Valentin V\"olkl}
\begin{description}
\item[] CERN
\item[] Espl. des Particules 1 - Geneva (Switzerland)
\item[] valentin.volkl@cern.ch
\end{description}

\subsection*{Education}
\begin{description}
    \item[] PhD in Particle Physics: 2021, Innsbruck University (Austria)
    \item[] Masters in Physics, 2015, Innsbruck University (Austria)
\end{description}

\subsection*{Professional Experience}
\begin{description}
    \item[] 2023--present: Systems Software Engineer, CERN (Switzerland)
\end{description}

\subsection*{Tools}

\begin{itemize}
    \item[] CVMFS: a scalable, reliable and low-maintenance software distribution service
    \\lead developer \& release manager (2023--present)
    \\{\small{\url{https://cernvm.cern.ch/fs} - \url{https://cvmfs.readthedocs.io}}}
    \item[] Key4hep: A full software stack for future collider experiments\\developer (2020-2023)\\{\small{ \url{https://github.com/key4hep/}}}
\end{itemize}

\subsection*{Conferences, Workshops and Tutorials}

\begin{itemize}


\item {{\emph "Key4hep: Progress on Common Software "}, Talk at { LCWS 2021}}\\
\item {{\emph "CERN R\&D on Spack and the Turnkey Stack"}, Talk at {HSF WLCG Virtual Workshop}}\\
\item {{\emph "First performance results for Liquid Argon Calorimetry for FCC-ee"}, Talk at { FCC Week 2019, Brussels}}\\
\item {{\emph " Combined reconstruction with tracker and calorimeter "}, Talk at { FCC Week 2019, Brussels}}\\
\item {{\emph "Timed Track Seeding to mitigate pile-up effects"}, Talk at FCC week
2018, Amsterdam} \\

\item[] \emph{Maintaining a Modern Scientific Software Stack Made Easy with EasyBuild} tutorial at ISC'21, June 2021 (\url{https://easybuild.io/tutorial/isc21})
\end{itemize}

\subsection*{Selected Publications}

\paragraph{Conference Papers}

\begin{itemize}

\item[] L. Promberger, V. V\"olkl, M. Harvey, J. Blomer, \emph {CernVM-FS at Extreme Scales}. Accepted for publication to CHEP 2023, Norfolk VA, USA.

\item[] {M. Mangano and others (FCC Collaboration). "{ \emph Future Circular Collider Conceptual
Design Report, Vol. 1 : Physics opportunities. }" Technical Report CERN-ACC-2018-0056, CERN, Geneva,
Dec 2018.  \url{http://cds.cern.ch/record/2651294}.  Submitted for publication to Eur. Phys. J. C.} \\

\item[] {M.  Benedikt  and  others  (FCC  Collaboration). "{\emph Future  Circular  Collider
Conceptual  Design  Report,  Vol.  2:  The  Lepton  Collider  (FCC-ee).}"   Technical Report
CERN-ACC-2018-0057, CERN, Geneva, Dec  2018.   \url{http://cds.cern.ch/record/2651299}.  Submitted for publication to Eur. Phys. J. ST.} \\

\item { M.  Benedikt  and  others  (FCC  Collaboration). "{\emph Future Circular Collider Conceptual Design Report, Vol. 3 : The Hadron Collider
(FCC-hh). }" CERN-ACC-2018-0058. Geneva: CERN. \url{http://cds.cern.ch/record/2651300}.} \\



\end{itemize}

